Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2020-04-15 thirdPaper/draft/typeConeAssociahedra.tex
win one page...

\vspace{1.5cm}
\centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
\vspace{.5cm}
\centerline{The type cone of the cluster fan of type~$A_2$.}

\newpage
\tableofcontents

@@

\newpage
\section*{Introduction}

@@

@@

\medskip
To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the geometric approach to scattering amplitudes that has flourished during the last years~\cite{ArkaniHamedTrnka-Amplituhedron,ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}. The kinematic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the most recent ``positive geometries''~\cite{ArkaniHamedBaiLam-PositiveGeometries} that has emerged in the study of scattering amplitudes.

@@

\newpage
\para{Schematic diagram of logical dependencies}

>>>>

%\vspace{1.5cm}
%\centerline{\includegraphics[scale=.8]{typeConeCoarsenings}}
%\vspace{.5cm}
%\centerline{The type cone of the cluster fan of type~$A_2$.}
%
%\newpage
\enlargethispage{.3cm}
\tableofcontents
\vspace{-.5cm}

@@

%\newpage
\section*{Introduction}

@@

\enlargethispage{.4cm}

@@

\medskip
\enlargethispage{.2cm}
To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the geometric approach to scattering amplitudes that has flourished during the last years~\cite{ArkaniHamedTrnka-Amplituhedron,ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}. The kinematic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the most recent ``positive geometries''~\cite{ArkaniHamedBaiLam-PositiveGeometries} that has emerged in the study of scattering amplitudes.

@@

%\newpage
\para{Schematic diagram of logical dependencies}
